Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-04-27 03_marlin_paper.qmd
initial fandf submission

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: chicago-author-date-16th-edition.csl
bibliography: references.bib
params:
  run_name: ["v1.0"]
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
---

@@

<!-- Single column, double line spaced -->

<!-- Within the word count (no more than 7000-8000 words for Standard Articles, 3000-4000 words for Applications and Practical Tools) -->

<!-- Continuous line and page numbering throughout -->

<!-- Clearly defined manuscript structure as standard: Author details, Abstract (must be numbered 1-4 according to Manuscript Specifications), Keywords, Introduction, Materials and Methods, Results, Discussion, Figures and Tables with captions -->

<!-- Figures and Tables can be embedded within the text where referenced to facilitate reviewing -->

<!--         Author Contributions (if >1 author – see Authorship Policy). -->

<!--         Statement of where you intend to archive your data -->

@@

Journal Name: Ecological Applications

Manuscript Type: Article

Manuscript Title: Simulating Benefits, Costs, and Tradeoffs of Management Policies in Marine Social-Ecological Systems

@@

Affiliations:
^1^ School of Aquatic and Fishery Sciences, University of Washington,1122 NE Boat St Box 355020,Seattle, WA, USA
^2^ Current Address: Inter-American Tropical Tuna Commission,8901 La Jolla Shores Drive, CA, USA
La Jolla, CA 92037, USA
^3^ Marine Science Institute, University of California, Santa Barbara, CA, USA
^4^ Bren School of Environmental Science & Management, University of California, Santa Barbara, CA, USA
^5^ Environmental Markets Lab, University of California, Santa Barbara, CA, USA
^6^ Habitat and Ecological Processes Research Program, Alaska Fisheries Science Center, NOAA, NMFS, NOAA, Seattle, WA, USA

Corresponding Author: Daniel Ovando <dovando@iattc.org>

Open Research Statement: All code and materials needed to reproduce this paper is available at [https://github.com/DanOvando/marlin-paper](https://github.com/DanOvando/marlin-paper).

Key Words: 
Bio-economic modeling, spatio-temporal modeling, marine protected areas, fisheries management, marine spatial planning, conservation planning

@@

@@

```{r}
#| label: fig-blue-ssb
#| fig-cap: Spawning biomass divided by unfished spawning biomass in the time period prior to implementation of MPAs for the pelagic case study."

@@

# Results

@@

# Discussion

@@

## Author Contribitions

Methods and code written by DO and JT. Results produced by DO. Data collected by EB and LT. All authors contributed to the conceptualization and writing of the manuscript.

## Conflit of Interest Statement

The authors declare no conflicts of interest.

>>>>

---
format:
  pdf:
    toc: false
    fig-pos: 'H'
    mainfont: Times New Roman
    sansfont: Times New Roman
    fontsize: 12pt
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
csl: apa-6th-edition.csl
bibliography: references.bib
params:
  run_name: ["v1.0"]
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
  - \usepackage{bm}
---

<!-- referees -->

<!-- Maya Tolstoy -->

<!-- Mikaela Provost -->

<!-- Leah Gerber -->

<!-- David M. Kaplan -->

@@

@@

Title: Simulating Benefits, Costs, and Tradeoffs of Spatial Management
in Marine Social-Ecological Systems

Running Title: Spatial Social-Ecological Simulation

@@

Affiliations: ^1^ School of Aquatic and Fishery Sciences, University of
Washington,1122 NE Boat St Box 355020,Seattle, WA, USA ^3^ Marine
Science Institute, University of California, Santa Barbara, CA, USA ^4^
Bren School of Environmental Science & Management, University of
California, Santa Barbara, CA, USA ^5^ Environmental Markets Lab,
University of California, Santa Barbara, CA, USA ^6^ Habitat and
Ecological Processes Research Program, Alaska Fisheries Science Center,
NOAA, NMFS, NOAA, Seattle, WA, USA

Corresponding Author: Daniel Ovando
[dovando\@iattc.org](mailto:dovando@iattc.org){.email}

Present Address: \^2 Inter-American Tropical Tuna Commission,8901 La
Jolla Shores Drive, La Jolla, CA 92037, USA

Author Contributions: Methods and code written by DO and JT. Results
produced by DO. Data collected by EB and LT. All authors contributed to
the conceptualization and writing of the manuscript.

Conflict of Interest Statement: The authors declare no conflicts of
interest.

@@

## Keywords

Bio-economic modeling, spatio-temporal modeling, marine protected areas,
fisheries management, marine spatial planning, conservation planning

## Table of Contents

1.  Introduction
2.  Methods
    1.  Model Summary
    2.  Fleet Dynamics
    3.  Population Model
    4.  Case Studies
3.  Results
    1.  Coral Reefs
    2.  Pelagic Systems
4.  Discussion
5.  Acknowledgements
6.  Data Availability Statement
7.  References

@@

```{r}
#| label: fig-blue-ssb
#| fig-cap: "Spawning biomass divided by unfished spawning biomass in the time period prior to implementation of MPAs for the pelagic case study."

@@

## Results

@@

## Discussion

@@

## Data Availability Statement

The code, novel code, data, and materials needed to reproduce the
results and all aspects of this manuscript are publicly available at
https://github.com/DanOvando/marlin-paper, with supporting novel code
available at https://github.com/DanOvando/marlin/. Upon acceptance, all
data, materials, code, and novel code needed to reproduce the results
and all aspects of this manuscript will be publicly available via GitHub
at https://github.com/DanOvando/marlin-paper and
https://github.com/DanOvando/marlin/ and through figshare at
https://figshare.com/articles/preprint/marlin-paper/21843582
